---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# remisc

## Overview

This package started as a collection of some very simple utility functions for
my own use. I created this package in part just to learn how to build a package.
I also built it to avoid having to source or paste in functions I use reasonably
often, but keep forgetting the exact code to recreate.

Over time, this package will also serve as a place to archive really useful
functions I find on blog posts or elsewhere, such as those from John Mount
of Win-Vector...at least until the authors make them available in their own
packages.

As such, most of the functions in this package were cribbed entirely, or 
adapted, from the work of others, including from *Advanced R, Wickham (2014)*,
stackoverflow questions, and the *R Project* documentation.

## Installation

There was a bug in R-3.4.0 that prevented installation of this package. You
will need to install R-3.4.1 or higher

```{r, eval = FALSE}
# Install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("arestrom/remisc")
```


